### 2022-05-30 chapters/04-chapter-4.tex
txs auto checkin

\subsubsection{Kasus SI4}
Dari gambar \ref{result_cpu_4} dan \ref{result_mem_4} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.071 \textit{core} dan Memory sebanyak 131.55 MiB.

>>>>

\subsubsection{Kasus SI4}
Dari gambar \ref{result_cpu_4} dan \ref{result_mem_4} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.059 \textit{core} dan Memory sebanyak 146.6 MiB.
